Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
naming 2nd time

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - depth of processing, retrival cues, uniqueness of encoding - Rewind ----> retrival cues
% http://www.psych.utoronto.ca/Neuropsychologylab/PDF/Depth%20of%20processing,%20retrieval%20cues,%20and.pdf
% go into introduction?
% come back to this section if time allows.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\textit{Rewind} recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones. Differing from previously studied hyperlapse creation techniques, such as the studies by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, \textit{Rewind} does not require any cinematic archives from the users, and it is computationally lightweight. \textit{Rewind} inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used). The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. The current version of \textit{Rewind} is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them. \textit{Rewind} can be accessed at [anonymized: url to rewind].  %\ref{fig:flowchart}

@@

% heather - add determination of home?
\subsection{Route Selection}
A user's geolocation tracking data includes latitude and longitude coordinates, and timestamps of when the user was at given coordinates. \textit{Rewind} expects JSON formatted data, and is also compatible with other location-based formats such as GPX. Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.

@@

\subsection{Sequence Creation}
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images. Considering each \textit{Rewind} sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline. Due to the timing constraint, Rewind instead adopts a simplified approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% heather - depth of processing, retrival cues, uniqueness of encoding - Rewind ----> retrival cues
% http://www.psych.utoronto.ca/Neuropsychologylab/PDF/Depth%20of%20processing,%20retrieval%20cues,%20and.pdf
% go into introduction?
% come back to this section if time allows.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Rewind system recreates the visual sensation of travelling down past routes using raw Google Location History data retrieved from location-tracking apps, including the default tracking behavior on Android phones. Differing from previously studied hyperlapse creation techniques, such as the studies by Kopft et al. and Joshi et al \cite{Kopf:2014:FHV:2601097.2601195, Joshi:2015:RHC:2809654.2766954}, Rewind system does not require any cinematic archives from the users, and it is computationally lightweight. Rewind inputs geolocation data, maps out tracked trajectories, and outputs photo-video pairs with Google Street View images (although other street side photo services may be used). The sceneries in each photo-video pair are customized for each user based on times of the day, meteorological conditions and seasonal changes when the route was taken, providing users with multi-dimensional temporal cues. The current version of Rewind system is a open-sourced, web-based application implemented with Google Maps API and third-party JavaScript libraries, and therefore does not transfer sensitive user data nor store them. Rewind can be accessed at [anonymized: url to rewind].  %\ref{fig:flowchart}

@@

% heather - add determination of home?
\subsection{Route Selection}
A user's geolocation tracking data includes latitude and longitude coordinates, and timestamps of when the user was at given coordinates. Rewind expects JSON formatted data, and is also compatible with other location-based formats such as GPX. Rewind generates location points for the user, using smart filtering based on visit frequencies to decrease the data noise and diversify the locations shown to the user.

@@

\subsection{Sequence Creation}
Each video recollection created by Rewind is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meteorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, pixel-wise adjustment was applied on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meteorological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques in real-time on large sets of images. Considering each Rewind sequence of images would contain two hundred frames, this process would take many hours per route, and it would be challenging to incorporate a large training dataset into the rendering pipeline. Due to the timing constraint, Rewind instead adopts a simplified approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.
